Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
evaluation

2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
For well-established vocabularies, vocabulary constraints are almost completely satisfied\footnote{e.g. only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
This demonstrates that data providers take account of the formal specifications of well-established vocabularies and therefore constraint formulation in general works.
For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
which indicates bad data quality with regard to the formal specifications of newly defined vocabularies.

\begin{hyp}
Data represented by well-established vocabularies corresponds to formal specifications of these vocabularies which demonstrates that constraint formulation in general works. 
\end{hyp}

\begin{hyp}
Data represented by newly developed vocabularies, in contrast, does not correspond to formal specifications of these vocabularies.
\end{hyp}

It is likely that a newly developed vocabulary is still subject of constant change
and that early adopters did not properly understand its formal specification.
Thus, published data may not be consistent with its current version.
In case newly developed vocabularies turn into well-established ones,
their formal specifications and intended semantics will be clearer to data providers as the community will also have more experience in publishing data conforming to this vocabulary. 
As a consequence, vocabulary constraints will be satisfied leading to better data quality.

>>>>

2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g. only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
which indicates bad data quality with regard to the formal specifications of vocabularies.

\begin{hyp}
Data represented by well-established vocabularies corresponds to formal specifications of these vocabularies which demonstrates that constraint formulation in general works. 
Data represented by newly developed vocabularies, in contrast, does not correspond to formal specifications of these vocabularies.
\end{hyp}

It is likely that a newly developed vocabulary is still subject of constant change
and that early adopters did not properly understand its formal specification.
Thus, published data may not be consistent with its current draft or version.
In case newly developed vocabularies turn into well-established ones,
data providers are experienced in publishing their data represented by these vocabularies, 
the formal specifications are more elaborated and therefore clearer to data providers. 
As a consequence, vocabulary constraints are satisfied which leads to better data quality.
